\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \href{#3}{\raisebox{-0.2\height}\faGithub\ \underline{\small#2}}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Hariharan Mudaliar} \\ \vspace{1pt}
    \href{https://tinyurl.com/hariharanmudaliar}{\raisebox{-0.2\height}\faLink\ \underline{tinyurl.com/hariharanmudaliar}} ~
    \href{https://linkedin.com/in/hariharan-mudaliar}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/hariharan-mudaliar}} ~
    \href{mailto:hrhn.mudaliar251@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{hrhn.mudaliar251@gmail.com}} ~
    
    \href{https://github.com/Ebullioscopic}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Ebullioscopic}} ~
    \href{tel:+919429199029}{\raisebox{-0.2\height}\faPhone\ +91 9429199029}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {SRM Institute of Science and Technology}{2022 -- 2026}
    {B. Tech, Computer Science and Engineering - Artificial Intelligence and Machine Learning, CGPA: 9.62}{Chennai, India}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Hebron Higher Secondary School}{2020 -- 2022}
    {PCM with Computer Technologies, 88\%}{Ahmedabad, India}
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Swift, Kotlin, Java, JavaScript, HTML/CSS, C, C++} \\
     \textbf{Technologies/Frameworks}{: Django REST, Graphene, Kafka, Transformers, Diffusers, TensorFlow, PyTorch, Keras, Nvidia RAPIDS (cuDF, cuML, cuGraph), Streamlit} \\
     \textbf{Developer Tools}{: Xcode, Android Studio, Git, VS Code, Jupyter, Firebase, Jenkins, CI/CD} \\
     \textbf{Cloud}{: AWS (EC2, S3, RDS, CloudFront, EBS, ELB, SageMaker), Firebase, Supabase} \\
     \textbf{Databases}{: MySQL, PostgreSQL, MongoDB, Redis} \\
     \textbf{Others}{: REST APIs, LangChain, Ollama, BootStrap-5, Tailwind-CSS, OpenCV, MediaPipe, GraphQL} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Infosys}{Apr 2025 -- May 2025}
      {iOS Developer Intern}{On Site - Mysuru}
      \resumeItemListStart
        \resumeItem{Developed a Generative AI Powered Hospital Management System with Django Backend.}
        \resumeItem{Implemented the frontend as a native iOS app using SwiftUI and Swift, ensuring a seamless and responsive user experience.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Samsung India}{Jan 2024 -- Jul 2024}
      {Research Intern}{Remote - Bengaluru}
      \resumeItemListStart
        \resumeItem{Developed a Generative AI Powered Web Scraped Offer Search Engine using LLaMA-3, LangChain, and HuggingFace Transformers under Samsung PRISM Worklet.}
        \resumeItem{Utilized Django and Streamlit for backend development and integrated machine learning models using TensorFlow and PyTorch.}
        \resumeItem{Implemented a cross-platform mobile interface with ReactJS and Tailwind-CSS for user-friendly interaction.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{TryIt} $|$ \emph{SwiftUI, Jetpack Compose, Django REST, Diffusers, ControlNet, SAM, FastAPI, Apache Kafka}}{}{https://github.com/Ebullioscopic/TryIt}
        \resumeItemListStart
          \resumeItem{Developed a Virtual Try On App enabling users to try on clothes, shoes, hairstyles, and more using an image, without physically trying them on.}
          \resumeItem{Implemented an A100 GPU server backend with FastAPI and Apache Kafka for efficient pipeline and streaming management.}
          \resumeItem{Utilized advanced generative models (Diffusers, ControlNet, SAM) along with AutoML for realistic and customizable virtual try-on experiences.}
        \resumeItemListEnd
\vspace{-10pt}
    \resumeProjectHeading
      {\textbf{DynamicIsland} $|$ \emph{Swift, SwiftUI, UIKit}}{}{https://github.com/Ebullioscopic/DynamicIsland}
      \resumeItemListStart
        \resumeItem{Enhanced the notch on MacBook M3 and M4 Pro devices with interactive widgets, transforming it into a control center for multitasking.}
        \resumeItem{Developed a set of customizable widget options, improving user experience for streamlined task management.}
      \resumeItemListEnd
      
    \resumeProjectHeading
        {\textbf{DARG – Dynamic Adaptive Resonance Grids} $|$ \emph{Dynamic Approximate Nearest Neighbor (ANN) Search Structure}}{}{https://github.com/Ebullioscopic/DARG}
        \resumeItemListStart
          \resumeItem{Designed a modular ANN framework (DARG) for high-throughput analytics, enabling fast, accurate nearest neighbor search in dynamic data environments.}
          \resumeItem{Engineered adaptive grid structures with LID-aware tuning and incremental PCA for efficient, scalable vector analytics and query routing.}
          \resumeItem{Optimized for streaming and update-heavy workloads, outperforming traditional ANN methods in flexibility, memory efficiency, and update cost.}
        \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PATENTS-----------
\section{Patent}
\resumeSubHeadingListStart
    \resumeSubheading
    {\textbf{Method and Device for Generating Personalized Content}}{\textbf{July 21, 2025}}
    {Indian Patent Application No. 202441067717}{Samsung Electronics Co., Ltd.}
    \resumeItemListStart
        \resumeItem{Provisional on: September 06, 2024}
        \resumeItem{Patent Granted for creating a Novel Retrieval Augmented Generation Model for Personalized Content Generation with any LLM, along with Image generated content.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{+5pt}
%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.credly.com/badges/80ab1c0f-a948-433c-a481-9a0140b2c667/public_url}{\faLink\ GitHub Foundations}}{GitHub}{}{Jun 2025}
    \vspace{-3pt}
    \resumeSubheading
      {\href{https://www.credly.com/badges/e5f7060e-c75f-463a-b1ee-a8597280c6d5/public_url}{\faLink\ NVIDIA-Certified Associate: Generative AI LLMs}}{NVIDIA}{}{Jan 2025}
    \vspace{-3pt}
    \resumeSubheading
      {\href{101053655OCI2024FNDCFA}{\faLink\ Oracle Cloud Infrastructure 2024 Certified Foundations Associate}}{Oracle}{}{Dec 2024}
    \vspace{-3pt} 
    \resumeSubheading
      {\href{https://coursera.org/verify/PMENMO64FT5M}{\faLink\ Principles of UI/UX Design}}{Meta}{}{Oct 2024}
    \vspace{-3pt}

    \resumeSubheading
      {\href{https://www.credly.com/go/xfY4rgIm}{\faLink\ AWS Academy Machine Learning Foundations}}{AWS Academy Graduate}{}{May 2023}

  \resumeSubHeadingListEnd

\vspace{-15pt}
%-----------AWARDS-----------
\section{Awards}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Winner - Standard Chartered Hackathon}{Apr 2025}
      {Standard Chartered Bank}{}
      \resumeItemListStart
        \resumeItem{Developed an Agentic AI Powered Optical Character Recognition and Retrieval Augmented Generation Model for extracting, transforming and loading data from Government ID Cards}
      \resumeItemListEnd
      
    \resumeSubheading
      {Winner - Remote Sensing AI Hackathon}{Mar 2024}
      {IEEE GRSS - NASA - SRMIST}{}
      \resumeItemListStart
        \resumeItem{Developed a Custom Transformer Architecture using the Metal Performance Shaders to process a Masking Algorithm for Burn Scars Dataset.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Gold Medalist - Research Day 2024}{Mar 2024}
      {SRM Institute of Science and Technology}{}
      \resumeItemListStart
        \resumeItem{Awarded the highest distinction for pioneering work in Generative AI powered Image Stitching Satellite Clusters for Defense Applications related to Reconnaissance.}
      \resumeItemListEnd

    \resumeSubheading
      {Winner - SRM Hackathon 8.0}{Mar 2024}
      {Multi College Hackathon by SRM Institute of Science and Technology}{}
      \resumeItemListStart
        \resumeItem{Developed a Generative AI Powered Geriatric Assistance Rover to help Youngsters take care of their elder family members while they're away from them}
      \resumeItemListEnd
      
    \resumeSubheading
      {Winner - FinTechz-AI 2024}{Jul 2024}
      {National AI-based Hackathon for FinTech Solutions}{}
      \resumeItemListStart
        \resumeItem{Developed a FinTech AI solution leveraging predictive analytics for loan risk assessment, winning the top position among over 500 participants.}
      \resumeItemListEnd

    \resumeSubheading
      {Kodekshetra 2023}{May 2023}
      {Hackathon by ThinkDigital Chapter SRM (National level)}{}
      \resumeItemListStart
        \resumeItem{Secured 1st place in a national-level coding contest, showcasing expertise in algorithmic problem-solving and time-efficient coding.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Silver Medalist - Digital Art Domain}{Oct 2023}
      {SRM Euphoria’23}{}
      \resumeItemListStart
        \resumeItem{Received recognition for exceptional work in digital art, highlighting creativity and advanced design skills.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{+5pt}
%-----------EXTRACURRICULAR-----------
\section{Extracurricular}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical Lead and Editor - SRM Hostels}{Jan 2023 -- May 2023}
      {Editor and Publisher of Hostel Magazines}{}
      
    \resumeSubheading
      {UI/UX and Generative AI Training Associate}{Aug 2023 -- Present}
      {CINTEL Association, SRMIST}{}
      
  \resumeSubHeadingListEnd

\end{document}
